---
title: "Salary Spatial Models NBA"
author: "Piotr Wojtalewicz"
date: "2023-03-15"
output: html_document
---

---
title: "Salary_in_American_sports"
author: "Piotr Wojtalewicz"
date: '2022-10-18'
output: html_document
---






```{r}
library(tidyverse)
library(stringr)
library(readr)
library(dplyr)
library(ggplot2)
library(modelr)
library(PerformanceAnalytics)
library(writexl)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
MLS_Salary_20222023 <- read.csv("C:/Users/piotr/OneDrive/Pulpit/Rozdział_2/23/MLS_salary_2223.csv", sep = ";")
```

```{r}
NBA_Salary_20222023 <- read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_salary_20222023.csv", sep = ";")
```



```{r}
NBA_Salary_2003_04 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_salary_20032004.csv",sep = ";", dec = ",")
NBA_Salary_2004_05 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_salary_20042005.csv",sep = ";", dec = ",")
NBA_Salary_2005_06 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_salary_20052006.csv",sep = ";", dec = ",")
NBA_Salary_2006_07 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_salary_20062007.csv",sep = ";", dec = ",")
NBA_Salary_2007_08 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_salary_20072008.csv",sep = ";", dec = ",")
NBA_Salary_2008_09 <- read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_salary_20082009.csv",sep = ";", dec = ",")
NBA_Salary_2009_10 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_salary_20092010.csv",sep = ";", dec = ",")
NBA_Salary_2010_11 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_salary_20102011.csv",sep = ";", dec = ",")
NBA_Salary_2011_12 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_salary_20112012.csv",sep = ";", dec = ",")
NBA_Salary_2012_13 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_salary_20122013.csv",sep = ";", dec = ",")
NBA_Salary_2013_14 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_salary_20132014.csv",sep = ";", dec = ",")
NBA_Salary_2014_15 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_salary_20142015.csv",sep = ";", dec = ",")
NBA_Salary_2015_16 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_salary_20152016.csv",sep = ";", dec = ",")
NBA_Salary_2016_17 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_salary_20162017.csv",sep = ";", dec = ",")
NBA_Salary_2017_18 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_salary_20172018.csv",sep = ";", dec = ",")
NBA_Salary_2018_19 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_salary_20182019.csv",sep = ";", dec = ",")
NBA_Salary_2019_20 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_salary_20192020.csv",sep = ";", dec = ",")
NBA_Salary_2020_21 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_salary_20202021.csv",sep = ";", dec = ",")
NBA_Salary_2021_22 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_salary_20212022.csv",sep = ";", dec = ",")

```

```{r}
NBA_player_statistics2003_04 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_total_statistic_20032004.csv",sep = ";", dec = ",")
NBA_player_statistics2004_05 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_total_statistic_20042005.csv",sep = ";", dec = ",")
NBA_player_statistics2005_06 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_total_statistic_20052006.csv",sep = ";", dec = ",")
NBA_player_statistics2006_07 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_total_statistic_20062007.csv",sep = ";", dec = ",")
NBA_player_statistics2007_08 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_total_statistic_20072008.csv",sep = ";", dec = ",")
NBA_player_statistics2008_09 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_total_statistic_20082009.csv",sep = ";", dec = ",")
NBA_player_statistics2009_10 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_total_statistic_20092010.csv",sep = ";", dec = ",")
NBA_player_statistics2010_11 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_total_statistic_20102011.csv",sep = ";", dec = ",")
NBA_player_statistics2011_12 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_total_statistic_20112012.csv",sep = ";", dec = ",")
NBA_player_statistics2012_13 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_total_statistic_20122013.csv",sep = ";", dec = ",")
NBA_player_statistics2013_14 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_total_statistic_20132014.csv",sep = ";", dec = ",")
NBA_player_statistics2014_15 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_total_statistic_20142015.csv",sep = ";", dec = ",")
NBA_player_statistics2015_16 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_total_statistic_20152016.csv",sep = ";", dec = ",")
NBA_player_statistics2016_17 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_total_statistic_20162017.csv",sep = ";", dec = ",")
NBA_player_statistics2017_18 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_total_statistic_20172018.csv",sep = ";", dec = ",")
NBA_player_statistics2018_19 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_total_statistic_20182019.csv",sep = ";", dec = ",")
NBA_player_statistics2019_20 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_total_statistic_20192020.csv",sep = ";", dec = ",")
NBA_player_statistics2020_21 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_total_statistic_20202021.csv",sep = ";", dec = ",")
NBA_player_statistics2021_22 <-read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_total_statistic_20212022.csv",sep = ";", dec = ",")

```


```{r}
NBA_player_statistics2003_04<- rename(NBA_player_statistics2003_04, NAME = Player)
NBA_player_statistics2004_05<- rename(NBA_player_statistics2004_05, NAME = Player)
NBA_player_statistics2005_06<- rename(NBA_player_statistics2005_06, NAME = Player)
NBA_player_statistics2006_07<- rename(NBA_player_statistics2006_07, NAME = Player)
NBA_player_statistics2007_08<- rename(NBA_player_statistics2007_08, NAME = Player)
NBA_player_statistics2008_09<- rename(NBA_player_statistics2008_09, NAME = Player)
NBA_player_statistics2009_10<- rename(NBA_player_statistics2009_10, NAME = Player)
NBA_player_statistics2010_11<- rename(NBA_player_statistics2010_11, NAME = Player)
NBA_player_statistics2011_12<- rename(NBA_player_statistics2011_12, NAME = Player)
NBA_player_statistics2012_13<- rename(NBA_player_statistics2012_13, NAME = Player)
NBA_player_statistics2013_14<- rename(NBA_player_statistics2013_14, NAME = Player)
NBA_player_statistics2014_15<- rename(NBA_player_statistics2014_15, NAME = Player)
NBA_player_statistics2015_16<- rename(NBA_player_statistics2015_16, NAME = Player)
NBA_player_statistics2016_17<- rename(NBA_player_statistics2016_17, NAME = Player)
NBA_player_statistics2017_18<- rename(NBA_player_statistics2017_18, NAME = Player)
NBA_player_statistics2018_19<- rename(NBA_player_statistics2018_19, NAME = Player)
NBA_player_statistics2019_20<- rename(NBA_player_statistics2019_20, NAME = Player)
NBA_player_statistics2020_21<- rename(NBA_player_statistics2020_21, NAME = Player)
NBA_player_statistics2021_22<- rename(NBA_player_statistics2021_22, NAME = PLAYER)
```

```{r}
NBA_player_statistics2019_20
NBA_player_statistics2020_21
NBA_player_statistics2021_22
```


```{r}
NBA_2003_04 <- right_join(NBA_Salary_2003_04, NBA_player_statistics2003_04, by = "NAME")
NBA_2004_05 <- right_join(NBA_Salary_2004_05, NBA_player_statistics2004_05, by = "NAME")
NBA_2005_06 <- right_join(NBA_Salary_2005_06, NBA_player_statistics2005_06, by = "NAME")
NBA_2006_07 <- right_join(NBA_Salary_2006_07, NBA_player_statistics2006_07, by = "NAME")
NBA_2007_08 <- right_join(NBA_Salary_2007_08, NBA_player_statistics2007_08, by = "NAME")
NBA_2008_09 <- right_join(NBA_Salary_2008_09, NBA_player_statistics2008_09, by = "NAME")
NBA_2009_10 <- right_join(NBA_Salary_2009_10, NBA_player_statistics2009_10, by = "NAME")
NBA_2010_11 <- right_join(NBA_Salary_2010_11, NBA_player_statistics2010_11, by = "NAME")
NBA_2011_12 <- right_join(NBA_Salary_2011_12, NBA_player_statistics2011_12, by = "NAME")
NBA_2012_13 <- right_join(NBA_Salary_2012_13, NBA_player_statistics2012_13, by = "NAME")
NBA_2013_14 <- right_join(NBA_Salary_2013_14, NBA_player_statistics2013_14, by = "NAME")
NBA_2014_15 <- right_join(NBA_Salary_2014_15, NBA_player_statistics2014_15, by = "NAME")
NBA_2015_16 <- right_join(NBA_Salary_2015_16, NBA_player_statistics2015_16, by = "NAME")
NBA_2016_17 <- right_join(NBA_Salary_2016_17, NBA_player_statistics2016_17, by = "NAME")
NBA_2017_18 <- right_join(NBA_Salary_2017_18, NBA_player_statistics2017_18, by = "NAME")
NBA_2018_19 <- right_join(NBA_Salary_2018_19, NBA_player_statistics2018_19, by = "NAME")
NBA_2019_20 <- right_join(NBA_Salary_2019_20, NBA_player_statistics2019_20, by = "NAME")
NBA_2020_21 <- right_join(NBA_Salary_2020_21, NBA_player_statistics2020_21, by = "NAME")
NBA_2021_22 <- right_join(NBA_Salary_2021_22, NBA_player_statistics2021_22, by = "NAME")
```


```{r}
Cross_Table2122<- NBA_2021_22 %>% summarize(group_by(TEAM))
```


```{r}
NBA_Salary_20182019 <- read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_salary_20182019.csv", sep = ";")
NBA_Total_Statistic_20182019 <- read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_total_statistic_20182019.csv", sep = ";", dec = ",")

```

```{r}
NBA_Total_Statistic_20182019 <- rename(NBA_Total_Statistic_20182019, NAME = Player)
```


### Load data with salary in NBA

```{r}
NFL <- read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NFL_salary_20222023.csv", sep = ";")
```

### Load data with salary in NFL

```{r}
NHL <- read_csv2("C:/Users/piotr/OneDrive/Pulpit/salary/NHL_salary_20222023.csv")
NHL$NAME<-gsub("\xa0", "", NHL$NAME)
```

### Load data with salary in NHL

```{r}
NBA_player_statistics20212022<- read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_total_statistic_20212022.csv", sep = ";")
NBA_player_statistics20202021<- read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_total_statistic_20202021.csv", sep = ";")
```

### Load date with personal statistics in 2021/2022 season

```{r}
NBA_team_statistics20212022 <- read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_team_statistics_20212022.csv", sep = ";")
```

### Load date with team statistics in 2021/2022 season

```{r}
NBA_value_teams <- read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NBA_value_team_20212022.csv", sep = ";")
```

### load date with value of NBA teams in bilions dollars

```{r}
NHL_value_teams <- read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NHL_value_team_20212022.csv", sep = ";")
```

### load date with value of NHL teams in bilions dollars

```{r}
NFL_value_teams <- read.csv("C:/Users/piotr/OneDrive/Pulpit/salary/NFL_team_value.csv", sep = ";")
```

### load date with value of NFL teams in bilions dollars

```{r}
NBA_Salary_20222023 <- rename(NBA_Salary_20222023, INDEX = RK)
NBA_Salary_20212022 <- rename(NBA_Salary_20212022, INDEX = RK)
NFL<- rename(NFL, INDEX = RK)
NHL<- rename(NHL, INDEX = RK)

```

```{r}
NBA_Salary_20222023 <- NBA_Salary_20222023 %>% mutate(Salary1000 = SALARY/1000)
NBA_Salary_20212022 <- NBA_Salary_20212022 %>% mutate(Salary1000 = SALARY/1000)
NFL <- NFL%>% mutate(Salary1000 = SALARY/1000)
NHL <- NHL%>% mutate(Salary1000 = SALARY/1000)
MLS_Salary_20222023 <- MLS_Salary_20222023 %>% mutate(Salary1000 = Salary/1000)
```

```{r}
NBA_Salary_20222023 %>% summarise(mean_salary1000 = mean(Salary1000), sd_salary1000 = sqrt(var(Salary1000)), median_salary1000= median(Salary1000), min_salary1000 = min(Salary1000), max_salary1000 = max(Salary1000))

summary(NBA_Salary_20222023$Salary1000)

NBA_Salary_20212022 %>% summarise(mean_salary1000 = mean(Salary1000), sd_salary1000 = sqrt(var(Salary1000)), median_salary1000= median(Salary1000), min_salary1000 = min(Salary1000), max_salary1000 = max(Salary1000))


NHL %>% summarise(mean_salary1000 = mean(Salary1000), sd_salary1000 = sqrt(var(Salary1000)), median_salary1000= median(Salary1000), min_salary1000 = min(Salary1000), max_salary1000 = max(Salary1000))

NFL %>% summarise(mean_salary1000 = mean(Salary1000), sd_salary1000 = sqrt(var(Salary1000)), median_salary1000= median(Salary1000), min_salary1000 = min(Salary1000), max_salary1000 = max(Salary1000))


  
```

```{r}
ggplot(NBA_Salary_20222023, aes(x = SALARY/1000))+ geom_histogram(binwidth = 2000, color="black", fill = "green") +
scale_x_continuous(name = "Salary NBA players", breaks= seq(0,50000,5000)) + ggtitle("Plot of salary in NBA") + theme_dark()+ 
scale_y_continuous(name = "Count of NBA players")

ggplot(NBA_Salary_20212022, aes(x = SALARY/1000))+ geom_histogram(binwidth = 2000, color="black", fill = "green") +
scale_x_continuous(name = "Salary NBA players", breaks= seq(0,50000,5000)) + ggtitle("Plot of salary in NBA") + theme_dark()+ 
scale_y_continuous(name = "Count of NBA players")

ggplot(NHL, aes(x = SALARY/1000))+ geom_histogram(binwidth = 1000, color="black", fill = "blue") +
scale_x_continuous(name = "Salary NHL players", breaks= seq(0,15000,2000)) + ggtitle("Plot of salary in NHL") + theme_dark()+ 
scale_y_continuous(name = "Count of NHL players") 
ggplot(NFL, aes(x = SALARY/1000))+ geom_histogram(binwidth = 5000, color="black", fill = "red") +
scale_x_continuous(name = "Salary NFL players", breaks= seq(0,230000,20000)) + ggtitle("Plot of salary in NFL") + theme_dark()+ 
scale_y_continuous(name = "Count of NFL players")


```


```{r}
NBA_plot1<-ggplot(NBA_Salary_20222023, aes(x = INDEX, y = Salary1000))+stat_smooth(size = 3)+ geom_point()
NBA_plot1 +theme_bw() +theme(legend.position = "none") + theme(text=element_text(size=15)) + ggtitle("Salary in thousands of dollars (2022/2023)")

NBA_plot1<-ggplot(NBA_Salary_20212022, aes(x = INDEX, y = Salary1000))+stat_smooth(size = 3)+ geom_point()
NBA_plot1 +theme_bw() +theme(legend.position = "none") + theme(text=element_text(size=15)) + ggtitle("Salary in thousands of dollars (2021/2022)")

```


```{r}
Atlanta_Hawks <- filter(NBA_Salary_20222023,TEAM== "Atlanta Hawks")
ggplot(Atlanta_Hawks, aes(x= Salary1000, y = NAME, shape = POSITION )) + geom_point() + labs (
title ="Salary players in Atlanta Hawks", 
subtitle = "(2022-2023)",
caption = "Data from ESPN webside")

Boston_Celtics <- filter(NBA_Salary_20222023,TEAM== "Boston Celtics")
ggplot(Boston_Celtics, aes(x= Salary1000, y = NAME, shape = POSITION )) + geom_point() + labs (
title ="Salary players in Boston Celtics", 
subtitle = "(2022-2023)",
caption = "Data from ESPN webside")

Brooklyn_Nets <- filter(NBA_Salary_20222023, TEAM == "Brooklyn Nets")
ggplot(Brooklyn_Nets, aes(x = Salary1000, y = NAME, shape = POSITION))+ geom_point()+ labs( 
title = ("Salary players in Brooklyn Nets "),
subtitle = "(2022-2023)",
caption = "Data from ESPN webside")

	
Charlotte_Hornets <- filter(NBA_Salary_20222023,TEAM== "Charlotte Hornets")
ggplot(Charlotte_Hornets, aes(x = Salary1000,y=NAME, shape= POSITION)) + geom_point() + labs (title = "Salary players in Charlotte Hornets")

Chicago_Bulls <- filter(NBA_Salary_20222023,TEAM== "Chicago Bulls")
ggplot(Chicago_Bulls, aes(x = Salary1000,y=NAME, shape= POSITION)) + geom_point() + labs (title = "Salary players in Chicago Bulls")

Cleveland_Cavaliers <- filter(NBA_Salary_20222023,TEAM== "Cleveland Cavaliers")
ggplot(Cleveland_Cavaliers, aes(x = Salary1000,y=NAME, shape= POSITION)) + geom_point() + labs (title = "Salary players in Cleveland Cavaliers")

Dallas_Maverics <- filter(NBA_Salary_20222023,TEAM== "Dallas Mavericks")
ggplot(Dallas_Maverics, aes(x = Salary1000,y=NAME, shape= POSITION)) + geom_point() + labs (title = "Salary players in Dallas Mavericks")

Denver_Nuggets <- filter(NBA_Salary_20222023,TEAM== "Denver Nuggets")
ggplot(Denver_Nuggets, aes(x = Salary1000,y=NAME, shape= POSITION)) + geom_point() + labs (title = "Salary players in Denver Nuggets")

Charlotte_Hornets <- filter(NBA_Salary_20222023,TEAM== "Charlotte Hornets")
ggplot(Charlotte_Hornets, aes(x = Salary1000,y=NAME, shape= POSITION)) + geom_point() + labs (title = "Salary players in Charlotte Hornets")

Detroit_Pistons <- filter(NBA_Salary_20222023,TEAM== "Detroit Pistons")
ggplot(Detroit_Pistons, aes(x = Salary1000,y=NAME, shape= POSITION)) + geom_point() + labs (title = "Salary players in Detroit Pistons")

Golden_State_Warriors <- filter(NBA_Salary_20222023,TEAM== "Golden State Warriors")
ggplot(Golden_State_Warriors, aes(x = Salary1000,y=NAME, shape= POSITION)) + geom_point() + labs (title = "Salary players in Golden State Warriors")

Houston_Rockets<- filter(NBA_Salary_20222023,TEAM== "Houston Rockets")
ggplot(Houston_Rockets, aes(x = Salary1000,y=NAME, shape= POSITION)) + geom_point() + labs (title = "Salary players in Houston Rockets")

Indiana_Pacers <- filter(NBA_Salary_20222023,TEAM== "Indiana Pacers")
ggplot(Indiana_Pacers, aes(x = Salary1000,y=NAME, shape= POSITION)) + geom_point() + labs (title = "Salary players in Indiana Pacers")

LA_Clippers <- filter(NBA_Salary_20222023,TEAM== "LA Clippers")
ggplot(LA_Clippers, aes(x = Salary1000,y=NAME, shape= POSITION)) + geom_point() + labs (title = "Salary players in 	LA Clippers")

Los_Angeles_Lakers <- filter(NBA_Salary_20222023,TEAM== "Los Angeles Lakers")
ggplot(Los_Angeles_Lakers, aes(x = Salary1000,y=NAME, shape= POSITION)) + geom_point() + labs (title = "Salary players in Los Angeles Lakers")

	
Memphis_Grizzlies <- filter(NBA_Salary_20222023,TEAM== "	Memphis Grizzlies")
ggplot(Memphis_Grizzlies, aes(x = Salary1000,y=NAME, shape= POSITION)) + geom_point() + labs (title = "Salary players in Memphis Grizzlies")

Miami_Heat<- filter(NBA_Salary_20222023,TEAM== "Miami Heat")
ggplot(Miami_Heat, aes(x = Salary1000,y=NAME, shape= POSITION)) + geom_point() + labs (title = "Salary players in Miami Heat")

	
Milwaukee_Bucks <- filter(NBA_Salary_20222023,TEAM== "Milwaukee Bucks")
ggplot(Milwaukee_Bucks, aes(x = Salary1000,y=NAME, shape= POSITION)) + geom_point() + labs (title = "Salary players in 
Milwaukee Bucks")

Minnesota_Timberwolves <- filter(NBA_Salary_20222023,TEAM== "Minnesota Timberwolves")
ggplot(Minnesota_Timberwolves, aes(x = Salary1000,y=NAME, shape= POSITION)) + geom_point() + labs (title = "Salary players in Minnesota Timberwolves")

New_Orleans_Pelicans <- filter(NBA_Salary_20222023,TEAM== "New Orleans Pelicans")
ggplot(New_Orleans_Pelicans, aes(x = Salary1000,y=NAME, shape= POSITION)) + geom_point() + labs (title = "Salary players in 	New Orleans Pelicans")

New_York_Knicks <- filter(NBA_Salary_20222023,TEAM== "New York Knicks")
ggplot(New_York_Knicks, aes(x = Salary1000,y=NAME, shape= POSITION)) + geom_point() + labs (title = "Salary players in New York Knicks")

Oklahoma_City_Thunder <- filter(NBA_Salary_20222023,TEAM== "Oklahoma City Thunder")
ggplot(Oklahoma_City_Thunder, aes(x = Salary1000,y=NAME, shape= POSITION)) + geom_point() + labs (title = "Salary players in Oklahoma City Thunder")

Orlando_Magic <- filter(NBA_Salary_20222023,TEAM== "Orlando Magic")
ggplot(Orlando_Magic, aes(x = Salary1000,y=NAME, shape= POSITION)) + geom_point() + labs (title = "Salary players in Orlando Magic")

Philadelphia_76ers <- filter(NBA_Salary_20222023,TEAM== "Philadelphia 76ers")
ggplot(Philadelphia_76ers, aes(x = Salary1000,y=NAME, shape= POSITION)) + geom_point() + labs (title = "Salary players in Philadelphia 76ers")

Phoenix_Suns <- filter(NBA_Salary_20222023,TEAM== "Phoenix Suns")
ggplot(Phoenix_Suns, aes(x = Salary1000,y=NAME, shape= POSITION)) + geom_point() + labs (title = "Salary players in Phoenix Suns")

Portland_Trail_Blazers <- filter(NBA_Salary_20222023,TEAM== "Portland Trail Blazers")
ggplot(Portland_Trail_Blazers, aes(x = Salary1000,y=NAME, shape= POSITION)) + geom_point() + labs (title = "Salary players in Portland Trail Blazers")

Sacramento_Kings <- filter(NBA_Salary_20222023,TEAM== "Sacramento Kings")
ggplot(Sacramento_Kings, aes(x = Salary1000,y=NAME, shape= POSITION)) + geom_point() + labs (title = "Salary players in Sacramento Kings")

San_Antonio_Spurs <- filter(NBA_Salary_20222023,TEAM== "San Antonio Spurs")
ggplot(San_Antonio_Spurs, aes(x = Salary1000,y=NAME, shape= POSITION)) + geom_point() + labs (title = "Salary players in San Antonio Spurs")

Toronto_Raptors <- filter(NBA_Salary_20222023,TEAM== "Toronto Raptors")
ggplot(Toronto_Raptors, aes(x = Salary1000,y=NAME, shape= POSITION)) + geom_point() + labs (title = "Salary players in Toronto Raptors")

Utah_Jazz <- filter(NBA_Salary_20222023,TEAM== "Utah Jazz")
ggplot(Utah_Jazz, aes(x = Salary1000,y=NAME, shape= POSITION)) + geom_point() + labs (title = "Salary players in Utah Jazz")

Washington_Wizards <- filter(NBA_Salary_20222023,TEAM== "Washington Wizards")
ggplot(Washington_Wizards, aes(x = Salary1000,y=NAME, color= POSITION)) + geom_point() + labs (title = "Salary players in Washington Wizards")

```



```{r}
Northwest_Salary_20222023 <- filter(NBA_Salary_20222023, TEAM == "Portland Trail Blazers" |  TEAM == "Utah Jazz"|  TEAM =="Denver Nuggets" |  TEAM =="Minnesota Timberwolves" |  TEAM =="Oklahoma City Thunder")
Southwest_Salary_20222023 <- filter(NBA_Salary_20222023, TEAM == "Dallas Mavericks" | TEAM == "Houston Rockets"| TEAM == "San Antonio Spurs"| TEAM == "Memphis Grizzlies")
Paciffic_Salary_20222023 <- filter(NBA_Salary_20222023, TEAM == "Phoenix Suns"| TEAM == "Golden State Warriors" | TEAM == "LA Clippers" | TEAM == "Los Angeles Lakers" | TEAM == "Sacramento Kings")
```
#podział na diwizje



```{r}
ggplot(Northwest_Salary_20222023, aes(x=Salary1000 , y= INDEX)) +geom_point() + facet_wrap(~TEAM)
ggplot(Southwest_Salary_20222023, aes(x=Salary1000 , y= INDEX)) +geom_point() + facet_wrap(~TEAM)
ggplot(Paciffic_Salary_20222023, aes(x=Salary1000 , y= INDEX)) +geom_point() + facet_wrap(~TEAM)

```

```{r}
Atlantic_Salary_20222023 <- filter(NBA_Salary_20222023, TEAM == "Boston Celtics"|  TEAM == "Brooklyn Nets"|  TEAM =="New York Knicks" |  TEAM =="Philadelphia 76ers" |  TEAM =="Toronto Raptors")
Southeast_Salary_20222023 <- filter(NBA_Salary_20222023, TEAM == "Orlando Magic"| TEAM == "Miami Heat"| TEAM == "Atlanta Hawks"| TEAM == "Charlotte Hornets"| TEAM == "Washington Wizards")
Central_Salary_20222023 <- filter(NBA_Salary_20222023, TEAM == "Milwaukee Bucks"| TEAM == "Indiana Pacers"| TEAM == "Chicago Bulls"| TEAM == "Cleveland Cavaliers"| TEAM == "Detroit Pistons")
```



```{r}
Northwest_Salary_20222023 %>% filter(POSITION == "PG")
Paciffic_Salary_20222023
Paciffic_Salary_20222023 %>% filter(POSITION == "PG")
Southwest_Salary_20222023  %>% filter(POSITION == "PG")

Atlantic_Salary_20222023 %>% filter(POSITION == "SG")
Southwest_Salary_20222023  %>% filter(POSITION == "SG")
Paciffic_Salary_20222023 %>% filter(POSITION == "SF")

Atlantic_Salary_20222023 %>% filter(POSITION == "SF")
Central_Salary_20222023 %>% filter(POSITION == "PF")
Northwest_Salary_20222023 %>% filter(POSITION == "PF")

Northwest_Salary_20222023 %>% filter(POSITION == "C")

Southwest_Salary_20222023  %>% filter(POSITION == "C")
```



```{r}
ggplot(Atlantic_Salary_20222023, aes(x=Salary1000 , y= INDEX)) +geom_point() + facet_wrap(~TEAM)
ggplot(Southeast_Salary_20222023, aes(x=Salary1000 , y= INDEX)) +geom_point() + facet_wrap(~TEAM)
ggplot(Central_Salary_20222023, aes(x=Salary1000 , y= INDEX)) +geom_point() + facet_wrap(~TEAM)

```



```{r}
plot(Washington_Wizards$INDEX,Washington_Wizards$Salary1000)
plot(Utah_Jazz$INDEX,Utah_Jazz$Salary1000)


```



```{r}
Atalanta_Hawks_sum<- sum(Atlanta_Hawks$Salary1000)

```

```{r}
NBA_Salary_20212022 %>% group_by(TEAM) %>%
  summarise(sum = sum(Salary1000))  
```





# drugi podpunkt drugiego rozdziału


```{r}
PG_Positions_Salary_20222023 <- NBA_Salary_20222023 %>% filter(POSITION == "PG") 
SG_Positions_Salary_20222023 <- NBA_Salary_20222023 %>% filter(POSITION == "SG") 
SF_Positions_Salary_20222023 <- NBA_Salary_20222023 %>% filter(POSITION == "SF") 
PF_Positions_Salary_20222023 <- NBA_Salary_20222023 %>% filter(POSITION == "PF") 
C_Positions_Salary_20222023 <- NBA_Salary_20222023 %>% filter(POSITION == "C") 
```

```{r}
 PG_Positions_Salary_20222023 <- PG_Positions_Salary_20222023 %>% mutate(Salary1000 = SALARY/1000)
 SG_Positions_Salary_20222023 <- SG_Positions_Salary_20222023 %>% mutate(Salary1000 = SALARY/1000)
 SF_Positions_Salary_20222023 <- SF_Positions_Salary_20222023 %>% mutate(Salary1000 = SALARY/1000)
 PF_Positions_Salary_20222023 <- PF_Positions_Salary_20222023 %>% mutate(Salary1000 = SALARY/1000)
 C_Positions_Salary_20222023 <- C_Positions_Salary_20222023 %>% mutate(Salary1000 = SALARY/1000)

```



```{r}
summary(PG_Positions_Salary_20222023$Salary1000)
summary(SG_Positions_Salary_20222023$Salary1000)
summary(SF_Positions_Salary_20222023$Salary1000)
summary(PF_Positions_Salary_20222023$Salary1000)
summary(C_Positions_Salary_20222023$Salary1000)
```

```{r}

a<-PG_Positions_Salary_20222023 %>% group_by(TEAM) %>% summarise(sum(Salary1000))
b<-SG_Positions_Salary_20222023 %>% group_by(TEAM) %>% summarise(sum(Salary1000))
c<-SF_Positions_Salary_20222023 %>% group_by(TEAM) %>% summarise(sum(Salary1000))
d<-PF_Positions_Salary_20222023 %>% group_by(TEAM) %>% summarise(sum(Salary1000))
e<-C_Positions_Salary_20222023%>% group_by(TEAM) %>% summarise(sum(Salary1000))

a
b
c
d
e


```


```{r}
PG_Positions_Salary_20222023 %>% group_by(TEAM) %>% summarise(mean(Salary1000))
SG_Positions_Salary_20222023 %>% group_by(TEAM) %>% summarise(mean(Salary1000))
SF_Positions_Salary_20222023 %>% group_by(TEAM) %>% summarise(mean(Salary1000))
PF_Positions_Salary_20222023 %>% group_by(TEAM) %>% summarise(mean(Salary1000))
C_Positions_Salary_20222023 %>% group_by(TEAM) %>% summarise(mean(Salary1000))

```


```{r}
PG_Positions_Salary_20222023 %>% group_by(TEAM) %>% count(TEAM)
SG_Positions_Salary_20222023 %>% group_by(TEAM) %>%count(TEAM)
SF_Positions_Salary_20222023 %>% group_by(TEAM) %>% count(TEAM)
PF_Positions_Salary_20222023 %>% group_by(TEAM) %>% count(TEAM)
C_Positions_Salary_20222023 %>% group_by(TEAM) %>%count(TEAM)
```


#2.3

```{r}
summary(NHL)
```


## skośność 
```{r}
NBA_skew <- skewness(NBA_Salary_20222023$SALARY)
NBA_skew
```

```{r}
NBA_skewness_plot <- NBA_Salary_20222023 %>% 
  ggplot(aes(x = Salary1000)) + stat_density(geom = "line", alpha = 1, colour = "cornflowerblue")
NBA_skewness_plot + ggtitle("Skośność wynagrodzeń w NBA")
```


```{r}
NHL_skew <- skewness(NHL$SALARY)
NHL_skew

NHL_skewness_plot <- NHL %>% 
  ggplot(aes(x = Salary1000)) + stat_count(geom = "line", alpha = 1, colour = "cornflowerblue")
NHL_skewness_plot + ggtitle("Skośność wynagrodzeń w NHL")
```


```{r}
NFL_skew <- skewness(NFL$SALARY)
NFL_skew

NFL_skewness_plot <- NFL %>% 
  ggplot(aes(x = Salary1000)) + stat_density(geom = "line", alpha = 1, colour = "cornflowerblue")
NFL_skewness_plot + ggtitle("Skośność wynagrodzeń w NFL")

```
```{r}
MLS_skew <- skewness(MLS_Salary_20222023$Salary1000)
MLS_skew

MLS_skewness_plot <- MLS_Salary_20222023 %>% 
  ggplot(aes(x =Salary1000 )) + stat_density(geom = "line", alpha = 1, colour = "cornflowerblue")
MLS_skewness_plot + ggtitle("Skośność wynagrodzeń w MLS")
```



```{r}
hist_NBA<- NBA_Salary_20222023$Salary1000
hist(hist_NBA, main = "Diagram skośności w NBA", xlab = "Wynagrodzenia w 1000$", ylab = "Ilość zawodników")
hist_NFL<- NFL$Salary1000
hist(hist_NFL, main = "Diagram skośności w NFL", xlab = "Wynagrodzenia w 1000$", ylab = "Ilość zawodników")
hist_NHL<- NHL$Salary1000
hist(hist_NHL, main = "Diagram skośności w NHL", xlab = "Wynagrodzenia w 1000$", ylab = "Ilość zawodników")
hist_MLS<- MLS_Salary_20222023$Salary1000
hist(hist_MLS, main = "Diagram skośności w MLS", xlab = "Wynagrodzenia w 1000$", ylab = "Ilość zawodników")


```

###3.3.
```{r}
NBA_player_statistics2021_22
```


```{r}
PG_Positions_Statistics_20212022 <- NBA_player_statistics2021_22 %>% filter(POSITION == "PG") 
SG_Positions_Statistics_20212022 <- NBA_player_statistics2021_22 %>% filter(POSITION == "SG") 
SF_Positions_Statistics_20212022 <- NBA_player_statistics2021_22 %>% filter(POSITION == "SF") 
PF_Positions_Statistics_20212022 <- NBA_player_statistics2021_22 %>% filter(POSITION == "PF") 
C_Positions_Statistics_20212022 <- NBA_player_statistics2021_22 %>% filter(POSITION == "C")
```



```{r}
PG_Positions_Statistics_20212022 <- PG_Positions_Statistics_20212022 %>% group_by(TEAM)
```

```{r}
SG_Positions_Statistics_20212022 <- SG_Positions_Statistics_20212022 %>% group_by(TEAM)
SF_Positions_Statistics_20212022 <- SF_Positions_Statistics_20212022 %>% group_by(TEAM)
PF_Positions_Statistics_20212022 <- PF_Positions_Statistics_20212022 %>% group_by(TEAM)
C_Positions_Statistics_20212022 <- C_Positions_Statistics_20212022 %>% group_by(TEAM)
```


```{r}
write_xlsx(PG_Positions_Statistics_20212022,"C:/Users/piotr/OneDrive/Pulpit/Rozdział_3/PG_Positions_Statistics_20212022.xlsx" )
```

```{r}
write_xlsx(SG_Positions_Statistics_20212022,"C:/Users/piotr/OneDrive/Pulpit/Rozdział_3/SG_Positions_Statistics_20212022.xlsx" )
write_xlsx(SF_Positions_Statistics_20212022,"C:/Users/piotr/OneDrive/Pulpit/Rozdział_3/SF_Positions_Statistics_20212022.xlsx" )
write_xlsx(PF_Positions_Statistics_20212022,"C:/Users/piotr/OneDrive/Pulpit/Rozdział_3/PF_Positions_Statistics_20212022.xlsx" )
write_xlsx(C_Positions_Statistics_20212022,"C:/Users/piotr/OneDrive/Pulpit/Rozdział_3/C_Positions_Statistics_20212022.xlsx" )
```


```{r}
write_xlsx(NBA_2021_22,"C:/Users/piotr/OneDrive/Pulpit/Rozdział_3/3_1/NBA_2021_22.xlsx" )
write_xlsx(NBA_2003_04,"C:/Users/piotr/OneDrive/Pulpit/Rozdział_3/3_1/NBA_2003_04.xlsx")
write_xlsx(NBA_2009_10,"C:/Users/piotr/OneDrive/Pulpit/Rozdział_3/3_1/NBA_2009_10.xlsx" )
write_xlsx(NBA_2020_21,"C:/Users/piotr/OneDrive/Pulpit/Rozdział_3/3_1/NBA_2020_21.xlsx" )
```



